---
title: "Give Me Gestalt! Final Paper"
output: html_document
---
## Bayesian Analysis
```{r}
library(tidyverse)
library(brms)
library(ggplot2)
library(ggpubr)

# read in the filtered csv results and select the columns needed for analysis
d = read_csv2("/Users/Mirijam/Documents/BachelorCognitiveScience/4.Semester/XPLab/Final_Project/GiveMeGestalt_Exp/GiveMeGestalt_filtered_results.csv") %>% 
  filter(trial_name %in% c("rating_scale_object", "rating_scale_like")) %>% 
  select(submission_id, trial_name, response, picture_nr, artist)

# cast data into appropriate type
d_wide = spread(d, key = trial_name, value = response) %>% 
  mutate(likeability = factor(rating_scale_like, ordered = T),
         objects = factor(paste0("C", rating_scale_object), ordered = T),
         artist = factor(artist),
         picture_nr = factor(picture_nr),
         submission_id = factor(submission_id),
         objects_forward = objects)

# inspect data
ggplot(d_wide, aes(x = objects, y= likeability)) + geom_jitter() + geom_smooth(method = "lm")
```
### Visual display of the data
```{r}
# absolute frequency of likeability and detecting objects
a <- ggplot(data=d)+
  geom_bar(mapping= aes(x = trial_name, fill = response), position = "dodge")
a
```

```{r}
# absolute frequency of likeability and detecting objects regarding the artists
b <- ggplot(data=d)+
  geom_bar(mapping= aes(x = trial_name, fill = response))+
  facet_wrap(~artist)
b
```

## Section 1: 
### the first three models treat the object-ratings as ordinal using the new brms monotonic models

### Hierarchical model with only fixed effects
```{r}
model_1 = brm(data = d_wide,
                formula = likeability ~ mo(objects),
                family=cumulative("logit")
)
model_1
plot(marginal_effects(model_1), categorical = T)
```

### Hierarchical model with by-item (pictures) and by-subject random intercepts
```{r}
model_2 = brm(data = d_wide,
                formula = likeability ~ mo(objects) + (1 | picture_nr) + (1 | submission_id),
                family=cumulative("logit")
)
model_2
plot(marginal_effects(model_2), categorical = T)
```

### Hierarchical model with by-subject random intercepts and fixed effect of artist
```{r}
model_3 = brm(data = d_wide,
                formula = likeability ~ mo(objects) + artist + (1 | submission_id),
                family=cumulative("logit")
)
model_3
plot(marginal_effects(model_3), categorical = T)
```

## Section 2: 
### the following three models treat the object-ratings as interval-scale/ metric

### Hierarchical model with only fixed effects
```{r}
model_4 = brm(data = d_wide,
        formula = likeability ~ as.double(objects),
        family=cumulative("logit")
)
model_4
plot(marginal_effects(model_4))
```

### Hierarchical model with by-item (pictures) and by-subject random intercepts
```{r}
model_5 = brm(data = d_wide,
        formula = likeability ~ as.double(objects) + (1 | picture_nr) + (1 | submission_id),
        family=cumulative("logit")
)
model_5
plot(marginal_effects(model_5))
```

### Hierarchical model with by-subject random intercepts and fixed effect of artist
```{r}
model_6 = brm(data = d_wide,
        formula = likeability ~ as.double(objects) + artist + (1 | submission_id),
        family=cumulative("logit")
)
model_6
plot(marginal_effects(model_6))
```

## Model comparison
```{r}
loo <- loo(model_1, model_2, model_3, model_4, model_5, model_6)
loo
```

## Frequentist Analysis: Pearson correlation
```{r}
data <- read_csv2("GiveMeGestalt_filtered_results.csv")
```

### Data formatting
```{r}
data_temp <- as_tibble(data) %>% mutate(response = as.integer(response))
data_temp

x <- filter(data_temp, trial_name == 'rating_scale_like') %>% 
  select(c('response', 'picture_nr'))%>% 
  group_by(picture_nr) %>% 
  summarise(response = mean(response))
# x
y <- filter(data_temp, trial_name == 'rating_scale_object') %>% 
  select(c('response', 'picture_nr')) %>% 
  group_by(picture_nr) %>% 
  summarise(response = mean(response))
# y

data_formatted <- merge(x,y, by = 'picture_nr')
# data_formatted
```

### Correlation test and regression graph
```{r}
ggscatter(data_formatted, x = "response.x", y = "response.y", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Detectability", ylab = "Liking")

res <- cor.test(data_formatted$response.x, data_formatted$response.y, 
                    method = "pearson")
res

# extract the p.value
res$p.value

# extract the correlation coefficient
res$estimate

# the amount of variance explained
res$estimate^2
```
